Drawing on the insights from Chapter~\ref{sr},
this chapter details the development of
a compartmental model of heterosexual HIV transmission in Eswatini.
The model aims to capture key determinants of heterosexual transmission dynamics, including
sex work, numbers of sexual partners, levels of condom use, anal sex, and ART scale-up.
The model was implemented in Python~v3.8.10 with Numpy~v1.22.2,
and solved numerically using 4th order Runge-Kutta \cite{Gill1951} using a timestep of 0.05 years.
Post-hoc analysis was conducted in R~v3.6.3.
All code and selected results are available on GitHub.%
\footnote{\label{foot:github}\hreftt{github.com/mishra-lab/hiv-fsw-art}}
\par
The remainder of this chapter is organized as follows:
\newcommand{\iref}[1]{\item[\sref{#1}]}
\begin{itemize}
  \iref{model.str} outlines the model \emph{structure} and notation, including
  the population stratifications and sexual partnership types considered.
  \iref{model.par} details the data, analyses, and assumptions used for model \emph{parameterization}
  --- \ie estimating prior distributions for model parameters, including:
  HIV initialization in Eswatini;
  HIV transmission probablies and modifiers thereof;
  progression rates through HIV stages and the ART cascade of care;
  analysis of primary survey data to distinguish higher \vs lower risk Swati FSW;
  risk group sizes, rates of turnover, sexual partnership numbers,
  sex frequencies, partnership durations, and mixing.
  \iref{model.cal} details the data, analyses, and assumptions used for model \emph{calibration}
  --- \ie inferring parameter posterior distributions,
  under which model outputs best match calibration targets, including:
  overall and (where possible) group-specific HIV prevalence, incidence, and ART cascade attainment.
  \iref{model.res} presents the \emph{results} of model calibration, including:
  posterior parameter distributions, comparison of model outputs \vs calibration targets, and
  a descriptive summary of modelled transmission dynamics over time.
  \iref{model.disc} provides \emph{discussion} on the contributions of the chapter
  and notes the limitations of the model.
\end{itemize}
