%===================================================================================================
\subsection{Sex Frequency \& Partnership Duration}\label{model.par.sex}
%---------------------------------------------------------------------------------------------------
\subsubsection{Sex Frequency}\label{model.par.sex.freq}
The Eswatini general population data sources \cite{SDHS2006,SHIMS1,SHIMS2}
did not report on frequency of sex. % yes they did, SDHS2006: Table 6.10 TODO
In South Africa, average numbers of sex acts per week per partnership (non-sex work)
was reported as mean 2.5~(IQR: 1--3) \cite{Delva2013},
with consistent reports across main/spousal partnerships and casual partnerships.
Sex frequency among South Africans per month overall (not per-partnership)
is also summarized in \cite[Figure~3.15]{Shisana2005},
which is roughly consistent with \cite{Delva2013}, but motivates a smaller lower bound.
Median sex frequency per partnership-year in 1998 Rakai, Uganda was
approximately 90 acts with the ``more frequent'' of concurrent partners, and
approximately 20 acts with the ``less frequent'' \cite{Morris2010}.
Considering these data,
I sampled the number of sex acts per year in main/spousal partnerships
$F_{p_{1}}$ from a gamma prior distribution with 95\%~CI (13,~156),
and a relative rate for casual partnerships $F_{p_{2}}/F_{p_{1}} \sim \opname{Unif}(0.5,1)$.
As described in \sref{model.par.sw.part},
I defined $F_{p_{3}} = 12$ for occasional sex work partnerships,
and $F_{p_{4}} \sim \opname{Unif}(12,36)$ for regular sex work partnerships.
I also constrained samples of $F_{p_{4}}$ such that
higher risk FSW never have commercial sex more than twice daily, on average.
% Coital frequency is not thought to be influenced by concurrent partnerships \cite{Delva2013}.
%---------------------------------------------------------------------------------------------------
\subsubsection{Anal Sex}\label{model.par.sex.anal}
Among Eswatini data sources, only \cite{EswKP2014} (FSW, 2014)
counted sex acts separately for anal and vaginal sex.
Among all FSW, the proportion of ``average sex acts per week'' that were anal (vs vaginal) was 2.9\%.
However, a previous coital diary study in neighbouring KwaZulu-Natal suggested
much higher proportions were anal \cite{Ramjee1999},
and face-to-face interview survey design may result in under-reporting \cite{Owen2020}.
Owen et al. review studies of anal sex in South Africa, and estimate that
0.6--16.5\% of sex acts among the general population are anal \cite{Owen2017}, \vs
2.4--15.9\% among FSW \cite{Owen2020}.
To reflect this greater uncertainty, the proportions of sex acts which are anal
in all partnerships were sampled from a gamma prior distribution with 95\%~CI (0.6,~16.5)\%.
%---------------------------------------------------------------------------------------------------
\subsubsection{Partnership Duration}\label{model.par.sex.dur}
As explored in Chapter~\ref{foi}, the durations of sexual partnerships
can be key determinants of epidemic dynamics and intervention impact.%
\footnote{Chapter~\ref{foi} also discusses the related phenomenon of partnership concurrency,
  including how concurrency is represented in compartmental models.}
Eswatini-specific data on partnership duration are lacking.
Moreover, accurate estimation of partnership duration remains challenging even when data exist,
due to censoring, truncation, and sampling biases \cite{Burington2010}.
Similar to challenges in estimating sex work duration (\sref{app.model.math.xdur}),
we must distinguish the definition of an ``average partnership'' as
(a) among all partnerships in a population over a given \emph{time period}, \vs
(b) among all partnerships in a population \emph{cross-section}.
Case (b) will be biased by partnership duration,
so the estimated mean duration will longer,
while case (a) reflects an unbiased estimate.%
\footnote{If case (a) durations are exponentially distributed,
  the durations in case (b) will be gamma-distributed with $\alpha = 2, \beta = \lambda$;
  thus the mean duration in case (b) will be $\alpha/\beta = 2\lambda$ (twice as long).}
The difference between the exponential distribution mean and median
should also be kept in mind (see \sref{app.model.math.exp}).
%---------------------------------------------------------------------------------------------------
\paragraph{Main/Spousal Partnerships}
Detailed data on marriage in Eswatini was only captured in 2006 \cite[Table~6.1]{SDHS2006}.
The median age of first marriage was 24.3 among women and 27.7 among men (26.0 overall).
Approximately 64\% of women and 88\% of men (76\% overall) who were ever married or living together
were in a union at age 50--54.
However, no data indicated whether any respondents had remarried or entered into a secondary union.
Among women aged 40--49, the most recent data on
median age of first marriage and proportions ever remarried were
33 years old and 6.6\% in South Africa,
20.9 and 3.7\% in Lesotho, and 18.7 and 28.4\% in Mozambique \cite{John2022};
such data may not capture non-marital secondary unions.
Thus, I assumed $\rho = {}$5--20\% of unions among EmaSwati aged 50--54 were secondary.
Considering that the modelled population only includes ages 15--49,
I then defined the mean durations of main/spousal partnerships as
$\delta_{p_{1}} =  (0.76 - \rho)\,(49 - 26) \in (14.5, 18.5)$ years.
\par
In some models, partnership duration is used to define both
the total numbers of sex acts per partnership and the partnership change rate (see \sref{foi.prior}).
This change rate might be overestimated by the above definition,
since the rate should also consider whether and when
divorced/separated individuals form \emph{new} main/spousal partnerships.
The change rate could even be tied to the modelled baseline and HIV-attributable mortality,
given that the majority of Swati unions ended via spousal death
(83\% of unions among women and 56\% among men by age 50--54) \cite{SDHS2006}.
% TODO: (?) add exit from "k=1" state, rate proportional to HIV-attrib-mort of opposite sex
For simplicity and consistency with prior approaches,
I used the effective duration of 14.5--18.5 years throughout (uniform prior).
%---------------------------------------------------------------------------------------------------
\paragraph{Casual Partnerships}
No data is available regarding durations of non-marital sexual partnerships in Eswatini,
and regional data on are also limited.
I synthesized the available partnership duration data from
South Africa \cite{Harrison2008,Hargreaves2009,Nguyen2015},
Rural Tanzania \cite{Nnko2004},
and four cities in Kenya, Zambia, Benin, and Cameroon \cite{Ferry2001}.
Based on these data, I defined a gamma prior distribution for
the mean duration of casual partnerships $\delta_{p_{2}}$ with 95\%~CI (0.25,~1.5) years,
roughly consistent with prior models \cite{Johnson2009}.
A gamma distribution was chosen \vs uniform or normal
to reflect non-uniform belief while preventing negative values.
%---------------------------------------------------------------------------------------------------
\paragraph{Sex Work Partnerships}
As noted in \sref{model.par.sw.part}, duration of occasional sex work partnerships
is ill defined, but can be defined to comprise a single sex act with $F_{p_{3}}\delta_{p_{3}} = 1$.
Data on regular sex work partnerships is severely limited, and
sometimes regular paying clients later become
non-paying emotional partners \cite{Voeten2007,Mbonye2022}.
Based on \cite{Voeten2002}, I defined a gamma prior distribution for
the mean duration of regular sex work partnerships $\delta_{p_{4}}$ with 95\%~CI (0.5,~2.0) years.
% TODO: is this too long given FSW turnover?
