\paragraph{Chapter~\ref{intro}}
I am the sole author, with guidance and feedback from Sharmistha Mishra.
\paragraph{Chapter~\ref{sr}}
Sharmistha Mishra and I conceptualized the study and developed the search strategy.
I performed the search, extracted the data, conducted the analysis, and generated the results.
Sharmistha Mishra and I drafted the main text and appendix.
Sharmistha Mishra, Rupert Kaul, and I reviewed the results and contributed to revisions.
\paragraph{Chapter~\ref{model}}
Sharmistha Mishra and I conceptualized and designed the model structure.
Huiting Ma, Linwei Wang, Stefan Baral, Carly Comins, and Sheree Schwartz provided feedback on the model design.
I led model parameterization and calibration, including
review of published data, design and implementation of bias adjustments, and original analysis of FSW survey data.
Huiting Ma, Linwei Wang, Rupert Kaul, and Sharmistha Mishra supported these aspects
with biostatistical and epidemiological expertise.
Bheki Sithole, Sindy Matse, Zandile Mnisi, Laura Muzart,
Stefan Baral, Carly Comins, Sheree Schwartz, Amrita Rao, Nikita Viswasam, Oluwasolape Olawore, and Sosthenes Ketende
provided feedback on parameters and calibration targets for Eswatini and FSW specifically.
Michael Escobar and Sharmistha Mishra supported design of model calibration, and interpretation of calibration results.
I implemented the model and generated the results.
Sharmistha Mishra and I drafted the main text and appendix.
\paragraph{Chapter~\ref{foi}}
Sharmistha Mishra and I conceptualized the review of prior approaches.
I led the review, designed the experiments, developed the new approach,
implemented all approaches and experiments in the model from Chapter~\ref{model}, and generated the results,
with guidance and feedback from Sharmistha Mishra.
Sharmistha Mishra and I interpreted the results, and drafted the main text and appendix.
\paragraph{Chapter~\ref{art}}
Sharmistha Mishra and I conceptualized the study and designed the experiments,
with input from Stefan Baral, Sheree Schwartz, Huiting Ma, and Linwei Wang.
I implemented the experiments in the model from Chapter~\ref{model}, and generated the results,
with guidance and feedback from Sharmistha Mishra and Michael Escobar.
Sharmistha Mishra, Stefan Baral, Rupert Kaul, Michael Escobar, Linwei Wang, Bheki Sithole, and I interpreted the results.
Sharmistha Mishra and I and drafted the main text and appendix.
\paragraph{Chapter~\ref{conc}}
I am the sole author, with guidance and feedback from Sharmistha Mishra.
